Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-26 paper/main.tex
discussion of prim. contrasts (AD & AV; individual)

\todo[inline]{Aziz: reduced activity only in left PPA, and only for famous
places vs famous faces; I think they ran their f-test on the average of the PPA
voxels! anyway: their analysis is complicated, yet not sophisticated}

% intro
Second, we analyzed data from the audio-description.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
information embedded in an exclusively auditory stimulus would correlate with
increased hemodynamic activity in the PPA.
% results
Group results of the AD stimulus' primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap that we gained from a
visual localizer experiment \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} who modeled events from on- to offset of
sentences (describing unknown and famous places and faces), we modeled events
from on- to offset of single words (that indicats the visual content to the
listener).
% conclusion
\citep{aziz2008modulation} found significantly increased activity in only the
left PPA and only for sentences describing famous places compared to famous
faces.\todo{averaged across voxels in PPA/FFA defined by localizer}
%
Contrary, our group results suggest that auditory spatial information
compared to non-spatial information correlates with bilaterally increased
activation in its anterior.\todo{any concluding statement?}

@@

@@

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}

\todo[inline]{We hypothesize[d] that an exclusively auditory stimulus can/could
localize the PPA in individual subjects, and thus substitute a visual experiment
be which would be more practicable to assess brain functions in visually
impaired persons.}

%
Since the annotation of the narrator's voice allowed us to better/cleaner/nicer
operationalize spatial perception than the movie's annotation, we here
hypothesized
% AD stimulus

% intro
To test if an auditory narrative could substitute a visual localizer experiment,
we also examined the results of the primary AD contrast on the level of
individual subjects.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
unilateral significant cluster in one subject.
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
% group vs individual
Results on an individual level reveal that significant cluster are located in
the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
a group level is not just a by-product of the averaging process but can reliably
be found in individual study participants.
% conclusion
Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
is in principle suitable to localize (the anterior part) of a higher-level
visual area in the majority of subjects.
% chose the best contrast in the future
Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
alternative contrasts (strict, relaxed, or simple contrast), future studies that
aim for individual diagnostics / ROI localization should also test more than one
contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
shitty}

\todo[inline]{discussion of individual differences? what do the results
suggest? Differences in alertness, attention to spatial information,
predisposition? ``capability'' to process auditory spatial information?}

\todo[inline]{individual ``preference'' to pay attention to
spatial infos (which contradicts statement above that attention is not a
prerequisite)}

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal hints about
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room or locale (\texttt{groom})
to non-spatial hints.
% we did not choose se\_new and se\_old
We did not choose the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
The categories \texttt{se\_new} and \texttt{se\_old} were actually
heterogeneous: they rarely contained whole and thus a vague verbal descriptions
of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
jungle'') but mostly landmarks or buildings, and also non-spatial hints (e.g.
``Jenny as a teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of holistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial hints.
% future studies
Hence, future studies might investigate if a homogenous category of wholistic
but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
homogenous categories of more specific verbal descriptions of landmarks (e.g.
``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
different levels of hemodynamic activity.

@@

\todo[inline]{yeah, we have shortcomings but, look, we have a pattern of
spatially restricted clusters across contrasts (and stimuli)}

@@

% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but also extending into more posterior brain
regions
\todo[inline]{cf. discussed shortcomings}

@@

\todo[inline]{makes sense because it goes full circle to general naturalistic
stimulus topic and makes transition to negative controls easier (which is
essentially also "natural stimuli, fuck yeah!}

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements\todo{could
already already be mentioned in discussion of primary contrasts}

@@

\subsubsection{random shower toughts}

@@

\todo[inline]{could be mentioned in a few sentences. But above topics a far too
much still; better embed somewhere above}

@@

>>>>

\todo[inline]{Aziz: reduced activity only in left PPA, and only for famous
places vs famous faces; I think they ran their f-test on the average of PPA
voxels defined by separate localizer}

% intro
Second, we analyzed data from the audio-description.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
information embedded in an exclusively auditory stimulus would correlate with
increased hemodynamic activity in the PPA.
% results
Group results of the AD stimulus' primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap that we gained from a
visual localizer experiment \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} who modeled events from on- to offset of
sentences (describing unknown and famous places and faces), we modeled events
from on- to offset of single words (that indicates the visual content to the
listener).
% conclusion
\citep{aziz2008modulation} found significantly increased activity in only the
left PPA and only for sentences describing famous places compared to famous
faces.\todo{average response across voxels in ROI}
%
Contrary, our group results suggest that auditory spatial information
compared to non-spatial information correlates with bilaterally increased
activation in its anterior.\todo{any concluding statement?}

@@

\todo[inline]{shorten the shortcoming; focus on ``opportunities'' for future research}

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal hints about
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room or locale (\texttt{groom})
to non-spatial hints.
% we did not choose se\_new and se\_old
We did not choose the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
The categories \texttt{se\_new} and \texttt{se\_old} were actually
heterogeneous: they rarely contained whole and thus a vague verbal descriptions
of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
jungle'') but mostly landmarks or buildings, and also non-spatial hints (e.g.
``Jenny as a teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of holistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial hints.
% future studies
Hence, future studies might investigate if a homogeneous category of wholistic
but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
homogeneous categories of more specific verbal descriptions of landmarks (e.g.
``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
different levels of hemodynamic activity.

@@

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}
%
Based on the fact that the annotation of speech still offered a more precise way
to operationalize the perception of spatial information then the annotation of
cuts and locations, we also hypothesized that data from the audio-description
could reveal the location of the PPA in individual persons.
%
To test if a auditory narrative could [in principle] substitute a visual
localizer experiment, we examined the individual results from the
audio-description's primary contrast.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
unilateral significant cluster in one subject.
% one threshold (and contrast) to rule them all
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
% group vs individual
Results on an individual level reveal that significant cluster are located in
the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
the group level is not just a by-product of the averaging process but can
reliably be found in individual study participants.
% conclusion
Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
is in principle suitable to localize (the anterior part) of a higher-level
visual area in the majority of subjects.
% chose the best contrast in the future
Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
alternative contrasts (strict, relaxed, or simple contrast), future studies that
aim for individual diagnostics / ROI localization should also test more than one
contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
shitty}

\todo[inline]{probably not really important but: what do results suggest
regarding individual differences?  Differences in alertness, attention to
spatial information, predisposition?  ``capability'' to process auditory spatial
information?}

@@

\todo[inline]{despite ad hoc approach in movie, ``non-perfect'' speech-anno,
and non-exhausting confound control, we have a pattern of spatially restricted
clusters across contrasts (and stimuli)}

@@

% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but also extending into more posterior brain
regions

@@

\todo[inline]{makes sense because it goes full circle to general naturalistic
stimulus topic and makes transition to negative controls easier}

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements.\todo{could
already be mentioned in discussion of primary contrasts}

@@

\todo[inlince]{concluding statement: essentially "natural stimuli, fuck yeah!;
re-use of existent data; using [and extending] an already existing annotation
for to operationalize a specific perceptual process}

@@

\todo[inline]{make this short; as expected almost everywhere null results ->

@@

\subsubsection{shower tought: changes in soundscape should also correlate with
PPA activity}
